%-------------------------
% Resume in LaTeX
% Based on: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{iftex}
\ifpdftex
  \input{glyphtounicode}
\fi

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\ifpdftex
  \pdfgentounicode=1
\fi

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small #1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectSubheading}[2]{
    \vspace{2pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemPlain}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Sooyoung Moon} & Email: \href{mailto:msy0128@gmail.com}{msy0128@gmail.com} \\
  \href{https://github.com/symoon94}{github.com/symoon94} & Mobile: +82-10-9473-5586 \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://www.upstage.ai/}{Upstage}}{Remote}
      {Team Lead, SolarBox}{Apr 2026 -- Present}
    \resumeSubSubheading
      {Tech Lead, SolarBox}{Aug 2025 -- Mar 2026}
    \resumeSubSubheading
      {Software Engineer}{Jun 2021 -- Jul 2025}

      \resumeProjectSubheading{On-premise AI Solution Platform}{Dec 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Autonomous Team Agent (Milchick)}
          {Manual briefings and Q\&A routing across 4+ teams created significant coordination overhead. Built a production Slack agent with \textbf{Solar/Claude} dual-LLM routing---Solar classifies intent, then routes to Claude CLI or Solar for execution---with eval test suite for quality assurance, knowledge system with selective context loading, and anti-leak protections. Also created reusable agent skills for account provisioning, license generation, and catalog management. Eliminated manual coordination and enabled self-service partner operations.}
        \resumeItem{Enterprise Portal Lead}
          {Partners had no self-service way to access AI solution packages, requiring manual handoff per customer. Led development from requirements gathering to production: \textbf{AWS CDK} dev/prod separation, \textbf{GitHub Actions} CI/CD, \textbf{i18n} (83-file English translation), role-based draft versioning, and ``Edit with Claude'' AI-assisted editing. Enabled global partner self-service across AWS, Azure, and Snowflake.}
        \resumeItem{SolarBox Catalog \& Release}
          {No centralized system existed for managing 50+ AI product versions across multi-tenant deployments. Built manifest API with search, pagination, and semantic versioning with CUDA suffix filtering; configured \textbf{Keycloak} SSO and \textbf{ClickHouse} migration tracking. Coordinated SolarBox 2.5 release across 4+ engineering teams, shipping 6 AI products to 3 cloud marketplaces simultaneously.}
        \resumeItem{Model Encryption Pipeline}
          {Manual encryption steps were bottlenecking catalog registration. Automated end-to-end LLM model encryption via GitHub Workflow, \textbf{Kubernetes} Job, and \textbf{Ansible}, with \textbf{AWS OIDC} for secure S3 artifact management and checksum verification. Eliminated all manual intervention from encryption through upload to verification.}
      \resumeItemListEnd

      \resumeProjectSubheading{Document AI Serving System}{Jul 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Async Inference System}
          {Synchronous-only inference couldn't scale for enterprise documents. Designed v1 with \textbf{SQS}/Lambda (SaaS) and RabbitMQ (On-prem), then simplified to v2 with \textbf{Asynq} (Go Redis queue) to reduce operational complexity. Cut async response time from 30s to 0.2s and 88-page processing from 21min to 4min. Now processes 160,000+ pages daily with \textbf{18x throughput} improvement over previous system.}
        \resumeItem{Service Stability}
          {A 10-month intermittent panic had defied debugging across the team. Traced the root cause to thread-unsafe \textbf{go-fitz} PDF library internals through systematic reproduction; applied application-level \textbf{Locking} as a targeted fix. Eliminated 10,000+ daily Segmentation Faults and reduced 500-error false alarms from 65/week to zero.}
      \resumeItemListEnd

      \resumeProjectSubheading{Document AI MLOps Platform}{Feb 2022 -- Aug 2023}
      \resumeItemListStart
        \resumeItem{Storage Optimization}
          {Customers ingesting 20,000+ images daily faced unacceptable UI load times. Analyzed query patterns and applied targeted indexing to the image ingestion pipeline, achieving \textbf{98\%} reduction in load time.}
        \resumeItem{Real-time Event System}
          {Model training, evaluation, and inference tasks had no progress visibility, forcing users to poll for status. Implemented \textbf{SSE}-based real-time event architecture for live tracking.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Arizona}{Tucson, AZ}
      {Bachelor of Science in Computer Science}{May 2021}
    \resumeSubheading
      {Kookmin University}{Seoul, South Korea}
      {Bachelor of Science in Advanced Fermentation Fusion Science and Technology}{Aug 2017}
  \resumeSubHeadingListEnd


%-----------PRESENTATIONS-----------------
\section{Presentations}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{From Junior Developer to Tech Lead} $|$ \emph{\href{https://www.slideshare.net/slideshow/from-junior-developer-to-tech-lead-leveraging-ai-for-leadership-and-team-impact/286718141}{Women Techmakers Korea 2026}}}{Mar 2026}
    \resumeProjectHeading
      {\textbf{Making it Roll with AI: Survival Skills for Small Teams} $|$ \emph{\href{https://www.slideshare.net/slideshow/gdg-incheon-2025-ai/284715174}{GDG Incheon DevFest 2025}}}{Nov 2025}
    \resumeProjectHeading
      {\textbf{From Job Prep to 5th Year at an AI Startup} $|$ \emph{\href{https://www.slideshare.net/slideshow/2025-ai-5/284715261}{Chung-Ang University Career Seminar}}}{Nov 2025}
    \resumeProjectHeading
      {\textbf{The Journey of Document AI} $|$ \emph{\href{https://www.slideshare.net/slideshow/mlops-api-solarbox-document-ai/283755773}{Jeju AI Conference}} $|$ \emph{\href{https://www.hanbit.co.kr/product/C2486251278}{Hanbit+ DevGround 2025}}}{Oct 2025}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
